---
title: "ODOTCOMM18"
author: "Megan Hepner"
date: "March 16, 2018"
output: html_document
---

| Classification     | Icon         | Metric | Data |
|:-------------------|--------------|--------|------|
| Focal species      | Blue Crab    | 
| Focal species      | Shrimp       |
| Focal              | Birds        |
| Focal              | D. Terrapin  | 
| Focal              | Snappers     |
| Foundation species | Oyster Reefs |
| Foundation species | Marsh        | 
| Invasive           | Nutria       |

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(vegan)
library(infographiq)
library(ggplot2)

```

#Blue Crabs 
Data refernce: NMFS Science and Technology <https://www.st.nmfs.noaa.gov/pls/webpls/MF_ANNUAL_LANDINGS.RESULTS> 
```{r Blue Crabs}
blue_crab = read_csv("data/crabs_nmfs.csv") 
```

#Shrimp 
Data reference: NMFS Science and Technology <https://www.st.nmfs.noaa.gov/pls/webpls/MF_ANNUAL_LANDINGS.RESULTS>
Species: Brown Shrimp, Pink Shrimp, Rock Shrimp, Royal Red Shrimp, Seabob Shrimp, White Shrimp, Roughneck Shrimp

```{r Shrimp}
shrimp = read_csv("data/shrimp_nmfs.csv") 
```

#Diamondback Terrapin Turtle 
Data reference: Seleman et al. 2014 <https://www.researchgate.net/publication/269112701_Distribution_and_Abundance_of_Diamondback_Terrapins_Malaclemys_terrapin_in_Southwestern_Louisiana> 
```{r Terrapin}

```

#Saltmarsh Vegetarian 
Data reference: Coral Reef Monitoring Program  <https://cims.coastal.louisiana.gov/fulltableexports.aspx> 
```{r Saltmarsh Vegetation}

marsh = read_csv("data/vegetation_common_random_cims_cleaned.csv")
#Parsed with column specification:
# cols(
#   Year = col_integer(),
#   Collection_Date = col_character(),
#   Community = col_character(),
#   Sample_Type = col_character(),
#   Vegetation_Type = col_character(),
#   Percent_Cover_Total = col_double(),
#   Scientific_Name_As_Currently_Recognized = col_character(),
#   Common_Name_As_Currently_Recognized = col_character(),
#   Percent_Cover = col_character(),
#   In_Out = col_character(),
#   Number_Planted = col_integer(),
#   Number_Alive = col_integer(),
#   Organization = col_character(),
#   Personnel = col_character(),
#   Comments = col_character())

vegetation = marsh %>%
  select(Year, Common_Name_As_Currently_Recognized, Scientific_Name_As_Currently_Recognized, Percent_Cover_Total) %>%
  group_by(Year, Common_Name_As_Currently_Recognized, Scientific_Name_As_Currently_Recognized) %>%
  summarize(percent_cover_mean = mean(Percent_Cover_Total))

```

#Oytster reefs 
Data reference: NMFS Science and Technology <https://www.st.nmfs.noaa.gov/pls/webpls/MF_ANNUAL_LANDINGS.RESULTS>
```{r Oyster Reefs}
oyster = read_csv("data/oyster_nmfs.csv")
```

#Birds
Data reference: ebirds 
```{r Birds}

```

#Nutria 
Data reference:
```{ Nutria}

```

#Snappers
Data reference: NMFS Science and Technology
Species: Black Snapper, Blackfin Snapper, Gray Snapper, Lane Snapper, Mutton Snapper, Queen Snapper, Red Snapper, Silk Snapper, Vermilion Snapper, Yellowtail Snapper
```{r Snappers}
snappers = read_csv("data/snapper_nmfs.csv")
```

#Saltmarsh Ecotone Infographic 
Code from marinebon <https://github.com/marinebon/infographiq> 
```{r Infographic}

svg_elements = read_csv("svg_elements.csv")
plot_indicators = read_csv("plot_indicators.csv")


```
