---
title: "ODOTCOMM18"
author: "Megan Hepner"
date: "March 16, 2018"
output: html_document
---

# Louisiana Saltmarsh Ecotone Infographic 

## Developed by Megan Hepner, Paige Byerly, and Bethann Garramon Merkle at [OceanDotComm](https://lumcon.edu/oceandotcomm/), a science commmunication workshop, supported by the Louisiana Universities Marine Consortium (LUMCON). 

## Objective: Develop an interactive infographic of the Louisiana bayou saltmarsh ecotone with enganging narrative to depict what the status and trend of key ecosystem species. 

| Species Classification | Icon                 | Metric                | Data    |
|:-----------------------|----------------------|-----------------------|-------- |
| Focal                  | Blue CrabS           | pounds, dollars       | NMFS    |
| Focal                  | Shrimp               | pounds, dollars       | NMFS    |
| Focal                  | Birds                | diversity, abundance  | eBIRD   |
| Focal                  | Snappers             | pounds, dollars       | NMFS    |
| Focal                  | Drums                | pounds, dollars       | NMFS    |
| Foundation             | Oyster Reefs         | pounds, dollars       | CIMS    |
| Foundation             | Marsh grass          | Mean percent cover    | CIMS    |
| Foundation             | Black Mangrove       | Mean percent cover    | CIMS    |
| Invasive               | Nutria               | Harvested tail        |         |
| Focal                  | Diamondback Terrapin | NA                    | No data |
| Focal                  | Bottlenose dolphin   | NA                    | No data |
| Focal                  | Cocahoe              | NA                    | No data |
| Focal                  | Fidler crab          | NA                    | No dara |
| Focal                  | Periwinkle snails    | NA                    | No data | 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(vegan)
library(infographiq)
library(ggplot2)
library(brew)
library(dygraphs)
library(lubridate)
library(servr)
library(rmarkdown)
library(stringr)
library(tools)
library(xts)
library(RColorBrewer)
library(geojsonio)

```

#Blue Crabs 
Data refernce: NMFS Science and Technology <https://www.st.nmfs.noaa.gov/pls/webpls/MF_ANNUAL_LANDINGS.RESULTS> 
```{r Blue Crabs}
blue_crab = read_csv("data/crabs_nmfs.csv") 
```

#Shrimp 
Data reference: NMFS Science and Technology <https://www.st.nmfs.noaa.gov/pls/webpls/MF_ANNUAL_LANDINGS.RESULTS>
Species: Brown Shrimp, Pink Shrimp, Rock Shrimp, Royal Red Shrimp, Seabob Shrimp, White Shrimp, Roughneck Shrimp

```{r Shrimp}
shrimp = read_csv("data/shrimp_nmfs.csv") 
```

#Saltmarsh Vegetarian 
Data reference: Coral Reef Monitoring Program  <https://cims.coastal.louisiana.gov/fulltableexports.aspx> 
Species: smooth cordgrass, common reed, saltgrass, saltmeadow cordgrass, turtleweed, needlegrass rush
```{r Saltmarsh Vegetation}

marsh = read_csv("data/vegetation_common_random_cims_cleaned.csv")

vegetation = marsh %>%
  select(Year, Common_Name, Scientific_Name, Percent_Cover_Total) %>%
  group_by(Year, Common_Name, Scientific_Name) %>%
  summarize(percent_cover_mean = mean(Percent_Cover_Total))

write_csv(vegetation, "Data/vegetation_summarized.csv")

black_mangroves = read_csv("data/black_mangroves_cims.csv")

black_mangroves = black_mangroves %>%
  select(Year, Common_Name, Scientific_Name, Percent_Cover_Total) %>%
  group_by(Year, Common_Name, Scientific_Name) %>%
  summarize(percent_cover_mean = mean(Percent_Cover_Total))

write_csv(black_mangroves,"data/black_mangroves_summarized.csv")

```

#Oytster reefs 
Data reference: NMFS Science and Technology <https://www.st.nmfs.noaa.gov/pls/webpls/MF_ANNUAL_LANDINGS.RESULTS>
```{r Oyster Reefs}
oyster = read_csv("data/oyster_nmfs.csv")
```

#Birds
Data reference: ebirds 
```{r Birds}

```

#Nutria 
Data reference:
```{r Nutria}
nutria = read_csv("data/nutria_summarized.csv")
```

#Fish
Data reference: NMFS Science and Technology
Snapper Species: Black Snapper, Blackfin Snapper, Gray Snapper, Lane Snapper, Mutton Snapper, Queen Snapper, Red Snapper, Silk Snapper, Vermilion Snapper, Yellowtail Snapper
Drums: Red Drum, Black Drum 
```{r Fish}
snappers = read_csv("data/snapper_nmfs.csv")

drums = read_csv("data/drums_nmfs.csv")
```
