---
title: "ODOTCOMM18"
author: "Megan Hepner"
date: "March 16, 2018"
output: html_document
---

| Classification     | Icon         | Metric | Data |
|:-------------------|--------------|--------|------|
| Focal species      | Blue Crab    | 
| Focal species      | Shrimp       |
| Focal              | Birds        |
| Focal              | D. Terrapin  | 
| Focal              | Snappers     |
| Foundation species | Oyster Reefs |
| Foundation species | Marsh        | 
| Invasive           | Nutria       |

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(vegan)
library(infographiq)
library(ggplot2)

```

#Blue Crabs 
Data refernce: NMFS Science and Technology <https://www.st.nmfs.noaa.gov/pls/webpls/MF_ANNUAL_LANDINGS.RESULTS> 
```{r Blue Crabs}
blue_crab = read_csv("data/crabs_nmfs.csv") 
```

#Shrimp 
Data reference: NMFS Science and Technology <https://www.st.nmfs.noaa.gov/pls/webpls/MF_ANNUAL_LANDINGS.RESULTS>
Species: Brown Shrimp, Pink Shrimp, Rock Shrimp, Royal Red Shrimp, Seabob Shrimp, White Shrimp, Roughneck Shrimp

```{r Shrimp}
shrimp = read_csv("data/shrimp_nmfs.csv") 
```

#Diamondback Terrapin Turtle 
Data reference: Seleman et al. 2014 <https://www.researchgate.net/publication/269112701_Distribution_and_Abundance_of_Diamondback_Terrapins_Malaclemys_terrapin_in_Southwestern_Louisiana> 
```{r Terrapin}

```

#Saltmarsh Vegetarian 
Data reference: Coral Reef Monitoring Program  <https://cims.coastal.louisiana.gov/fulltableexports.aspx> 
Species: smooth cordgrass, common reed, saltgrass, saltmeadow cordgrass, turtleweed, needlegrass rush
```{r Saltmarsh Vegetation}

marsh = read_csv("data/vegetation_common_random_cims_cleaned.csv")

vegetation = marsh %>%
  select(Year, Common_Name, Scientific_Name, Percent_Cover_Total) %>%
  group_by(Year, Common_Name, Scientific_Name) %>%
  summarize(percent_cover_mean = mean(Percent_Cover_Total))

write_csv(vegetation, "Data/vegetation_summarized.csv")

black_mangroves = read_csv("data/black_mangroves_cims.csv")

black_mangroves = black_mangroves %>%
  select(Year, Common_Name, Scientific_Name, Percent_Cover_Total) %>%
  group_by(Year, Common_Name, Scientific_Name) %>%
  summarize(percent_cover_mean = mean(Percent_Cover_Total))

write_csv(black_mangroves,"data/black_mangroves_summarized.csv")

```

#Oytster reefs 
Data reference: NMFS Science and Technology <https://www.st.nmfs.noaa.gov/pls/webpls/MF_ANNUAL_LANDINGS.RESULTS>
```{r Oyster Reefs}
oyster = read_csv("data/oyster_nmfs.csv")
```

#Birds
Data reference: ebirds 
```{r Birds}

```

#Nutria 
Data reference:
```{ Nutria}

```

#Fish
Data reference: NMFS Science and Technology
Snapper Species: Black Snapper, Blackfin Snapper, Gray Snapper, Lane Snapper, Mutton Snapper, Queen Snapper, Red Snapper, Silk Snapper, Vermilion Snapper, Yellowtail Snapper
Drums: Red Drum, Black Drum 
```{r Fish}
snappers = read_csv("data/snapper_nmfs.csv")

drums = read_csv("data/drums_nmfs.csv")
```

#Saltmarsh Ecotone Infographic 
Code from marinebon <https://github.com/marinebon/infographiq> 
```{r Infographic}

#svg_elements = read_csv("svg_elements.csv")
#plot_indicators = read_csv("plot_indicators.csv")

Saltmarsh_ecoton_infographic = create_info_site(
  path_root = ".",
  dir_svg = "svg",
  elements_csv = "svg_elements.csv",
  indicators_csv = "plot_indicators.csv",
  site_title = "Louisiana Saltmarsh Ecotone Infographic",
  dir_rmd = "rmd",
  dir_web = "docs",
  svg_paths = list.files(file.path(path_root, dir_svg), ".*\\.svg$", full.names = T),
  svg_names = tools::file_path_sans_ext(basename(svg_paths)),
  site_yml_brew = system.file("site_template/_site.yml.brew",
  package =
  "infographiq"),
  index_md_brew = system.file("site_template/index.md.brew",
  package = "infographiq"),
  readme_md_brew = system.file("site_template/README.md.brew", package =
  "infographiq"),
  header = system.file("site_template/_header.html", package =
  "infographiq"),
  footer = system.file("site_template/_footer.html", package =
  "infographiq"),
  styles_css = system.file("site_template/styles.css", package
  = "infographiq"),
  render_modals = T,
  preview_site = T
  )

```
