---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "bluecrabs"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/mhepner90/LUMCON_ODOTCOMM18/master/prep/data/crabs_nmfs.csv",
        title   = "Annual Commercial Blue Crabs Pounds",
        y_label = "Pounds",
        col_t   = "Year",
        col_y   = "Pounds"
        #skip_lines
        #group_by  
        #std_err   
        , filter="Species==\"Blue Crab\""
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/mhepner90/LUMCON_ODOTCOMM18/master/prep/data/crabs_nmfs.csv",
        title   = "Annual Commercial Blue Crabs Dollars",
        y_label = "U.S. Dollars",
        col_t   = "Year",
        col_y   = "Dollars"
        #skip_lines
        #group_by  
        #std_err   
        , filter="Species==\"Blue Crab\""
    ),
    error = function(e) e
)
```
**Blue Crab (*Callinectes sapidus*)**
 
Figure 1: Louisiana’s annual commercial harvest of blue crab (*Callinectes sapidus*), represented as total pounds harvested/year, 1950-2016
 
Figure 2: Commercial value of Louisiana’s annual blue crab harvest (*Callinectes sapidus*), represented by US dollars, 1950-2016
 
Louisiana has the largest blue crab fishery in the world, and the species has enormous economic and cultural importance for the state. Blue crabs breed offshore, but their larvae swim inland to coastal marshes and estuaries. There, they mature before returning to open waters to spawn. Blue crabs play roles as both predator and prey in the ecosystem, making them an significant marsh species. As predators, they consume pretty much anything edible, helping to keep the marsh clean and free of detritus. As prey, they are food for wading birds and commercially-important pelagic fish species like red drum. Blue crab harvest yields declined following the Deepwater Horizon oil spill in 2010, but rebounded in the years after. The quick recovery may be attributed to temporary fisheries closures directly after the spill, which allowed crab stocks time to replenish. 
 
**References**: Fisheries data compiled from the NOAA National Marine Fisheries Service Annual Commercial Landing Statistics, via:
(https://www.st.nmfs.noaa.gov/commercial-fisheries/commercial-landings/annual-landings/index)
 
Bourgeois, M., J. Marx, K. Semon. 2014. Louisiana Blue Crab Fishery Management Plan. Louisiana Department of Wildlife and Fisheries Office of Fisheries.
(http://www.wlf.louisiana.gov/sites/default/files/pdf/page/37762-fishery-management-plans-marine/finalbluecrabfmp11-7-14.pdf)
 
