---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "nutria"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/mhepner90/LUMCON_ODOTCOMM18/master/prep/data/nutria_summarized.csv",
        title   = "Annual Nutria Harvest",
        y_label = "Number of Tails Collected",
        col_t   = "Year",
        col_y   = "Tails_Collected"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/mhepner90/LUMCON_ODOTCOMM18/master/prep/data/nutria_summarized.csv",
        title   = "Estimated Herbivory Damage",
        y_label = "Estimated Herbivory Damage (acres)",
        col_t   = "Year",
        col_y   = "Estimated_Herbivory_Damage_acres"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```
## Nutria (*Myocastor coypus*)

Figure 1: Total number of nutria harvested and submitted to the Louisiana Department of Wildlife and Fisheries (November-March) for bounty from 2002-2016 (as represented by tails collected).

Figure 2: Estimated total amount of marsh vegetation damaged by nutria per year. Herbivory damage is reported in acres, and is extrapolated from yearly aerial surveys of wetland transects in coastal Louisiana (defined as the region bounded by the Interstates 10 and 12 from the Texas to Mississippi state lines).

Nutria are wetland rodents related to beavers, and are native to South America. They feed on primarily on grass roots, although their diets have been found to include items as varied as bird eggs, and can eat 25% of their body weight in a day. Nutria were introduced to Louisiana in the 19th century as a farmed furbearer. Over time, escaped nutria became established in Louisiana’s vast wetland ecosystems, where they now contribute significantly to wetland loss. In Louisiana’s coastal marshes, nutria eat the roots of stabilizing grasses that retain soils and other substrates necessary for maintaining the marsh complex. The plants die when the roots are consumed, and foraging nutria can rapidly turn healthy marsh into open water. In Louisiana, wetland destruction by nutria was extensive until the initiation of the Coastwide Nutria Control Program in 2002, which pays local trappers a bounty for harvested nutria. The program has successfully reduced the amount of damage caused by nutria and their numbers have stabilized statewide.

**Reference**: CNCP/CWPRA/LDWF. Nutria data obtained via the Coastwide Nutria Control Program (CNCP), which is overseen by the Louisiana Department of Wildlife and Fisheries (LDWF) and funded through the Coastal Wetlands Planning, Protection, and Restoration Act (CWPPRA)
